---
title: "W_UP_01"
author: "Omar Challan"
date: "Spring 2024"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->



```{r}
boxplot(pushups~position,data=mydata)
```


I'm looking at the columns in the chart above, the left are the line positions, and on the right are the skilled positions. The height of the skilled box is much higher. The 25th Percentile on the skilled players is higher than the 75th Percentile of the line players. This seems to indicate that skilled positions can do more push-ups than line positions.


### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->


```{r}
favstats(pushups~position,data=mydata)
```


The average number of pushups that a line player can do is about one third the amount of an average skilled player.


## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


```{r}
t.test(pushups~position,data=mydata)
```



p-value = 0.000009421
 
The p-value is far smaller that 0.05 indicated that there is a strong statistical significance.
This rejects the $H_0$ leaving only the $H_A$.  



# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->


$H_0$ = There is no difference in push-ups based on position.
$H_A$ = There is a difference in push-ups based on position.

With assistance from ChatGPT, I was ablt to write some R code to Create a box plot.

Also, by using the Numerical-Cat helper tool, I was able to perform a T Test and a Summary of the data  with (favstats).

The box plot in conjunction with the summary and T test show that we can reject the $H_0$ leaving only the $H_A$.




